%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvskills}

%---------------------------------------------------------
  \cvskill
    {In prog.} % Category
    {\textbf{J.J. Millar}, P.Psychas, B. Abuaku, P. Amratia, K. Koram, K.B. Toh, D. Valle. Assessing and projecting the role of distance from local health facilities on early childhood malaria: a case example from northern Ghana. \textit{In progress}.} % Citation
    
\cvskill
    {} % Category
    {D. Valle, K.B. Toh, and \textbf{J.J. Millar}. Emergence of software for rapid prototyping of decision support tools by conservation scientists. \textit{Conservation Biology}. In review.} % Citation
    
\cvskill
    {} % Category
    {\textbf{J.J. Millar}, K.B. Toh, D. Valle. To screen or not to screen: an interactive framework for comparing cost-effectiveness of mass screening and treatment of malaria. \textit{Malaria Journal. In review.}} % Citation
    
\cvskill
    {} % Category
    {P. Amratia, P. Psychas, B. Abuaku, C. Ahorlu, \textbf{J.J. Millar}, S. Oppong, K. Koram, and D.R. Valle. 2018. Using a Bayesian geostatistical model to characterize local-scale heterogeneity of malaria risk in Bunkpurugu-Yunyoo district in northern Ghana. \textit{Am. J. Trop. M. Hyg.. In review.}
} % Citation

%---------------------------------------------------------
  \cvskill
    {2018} % Year
    {\textbf{Millar, J.J.}, P. Psychas, P. Amratia, B. Abuaku, C. Ahorlu, K. Koram, S. Oppong, and D. Valle. 2018. “\href{https://malariajournal.biomedcentral.com/articles/10.1186/s12936-018-2491-2}{Detecting local risk factors for residual malaria in northern Ghana using Bayesian model averaging}”. \textit{Malaria Journal} 17:343.} 

%---------------------------------------------------------
\cvskill
    {2017} % Year
    {Payne, J.T., \textbf{J.J. Millar}, C. Jackson, and C. Ochs. 2017. “\href{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0174890}{Patterns of variation in diversity of the Mississippi river microbiome over 1,300 kilometers}”. \textit{PLoS ONE} 12(3): e0174890.} 

%---------------------------------------------------------

\cvskill
    {2016} % Year
    {Valle, D.R., \textbf{J.J. Millar}, and P. Amratia. 2016. “\href{https://malariajournal.biomedcentral.com/articles/10.1186/s12936-016-1565-2}{Spatial heterogeneity can undermine the effectiveness of country-wide test and treat policy for malaria: a case study from Burkina Faso}”. \textit{Malaria Journal} 15: 513.} 

%---------------------------------------------------------

\cvskill
    {2015} % Year
    {Valle, D.R., J.M. Tucker-Lima, \textbf{J.J. Millar}, P. Amratia, and U. Haque. 2015. “\href{https://malariajournal.biomedcentral.com/articles/10.1186/s12936-015-0966-y}{Bias in logistic regression due to imperfect diagnostic test results and practical correction approaches}”. \textit{Malaria Journal} 14: 434.
    } 
    
\cvskill
    {} % Year
    {\textbf{Millar, J.J.}, J.T. Payne, C.A. Ochs, and C.R. Jackson. 2015. “\href{http://aem.asm.org/content/early/2014/09/08/AEM.01844-14}{Particle-associated and cell-free extracellular enzyme activity in relation to nutrient status of large tributaries of the Lower Mississippi River}”. \textit{Biogeochemistry} 124(1-3): 255-271.
    } 

%---------------------------------------------------------
\cvskill
    {2014} % Year
    {Jackson, C.R., \textbf{J.J. Millar}, J.T. Payne, and C.A. Ochs. 2014. “\href{http://aem.asm.org/content/early/2014/09/08/AEM.01844-14}{Free-living and particle-associated bacterioplankton in large rivers of the Mississippi River Basin demonstrate biogeographic patterns}”. Applied and \textit{Environmental Microbiology} 80(23); 7186-7195.
    } 

%---------------------------------------------------------
\cvskill
    {2013} % Year
    {Jackson, C.R., H.L. Tyler, and \textbf{J.J. Millar}. 2013. “\href{https://www.jove.com/video/50399/determination-microbial-extracellular-enzyme-activity-waters-soils}{Determination of Microbial Extracellular Enzyme Activity in Waters, Soils, and Sediments using High Throughput Microplate Assays}”. \textit{Journal of Visualized Experiments} 80: 50399.
    } 

%---------------------------------------------------------



\end{cvskills}

{Reviewer: Ecological Applications}
\\
\\